A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-14 doc/Paper1/ms.tex
Phil's affiliation

\title[Measuring Time Delays]
{A Model for Extracting Time Delays from Noisy Time Series Data} 
\author[B. J. Brewer]{Brendon J. Brewer$^1$, Philip J. Marshall$^2$\\
$^1$Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand\\
$^2$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK}

>>>>

\title[Measuring Time Delays]
{A Model for Extracting Time Delays from Noisy Time Series Data} 
\author[B. J. Brewer]{Brendon J. Brewer$^1$, Philip J. Marshall$^2$\\
$^1$Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand\\
$^2$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
